---
title: "Check values against SQL query versions of the same thing"
author: "M Siple"
date: "2023-01-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Setup channel to connect to Oracle --------------------------------------
source(here::here("R/setup_channel.R"))
# The setup_channel.R script sets up a channel using your Oracle username and pw.

# Get report settings -----------------------------------------------------
source("R/00_report_settings.R")

# Functions, packages, directories ---------------------------------------------
source("R/01_directories.R")
source("R/02_load_packages.R") 
```
# Check Table 1

Insert script here for checking between my table and others!

```{r}
# FROM NED ISSUE #24. ALSO LOOK AT R/Tbl1Fxn.R which Ned sent and I modified.
# -- SQLPlus for Table 1 (historic)
# create or replace view DATA_REPORT_TABLE_1 as
# select a.INPFC_AREA,
# a.DEPTH_RANGE,
# STATIONS_ALLOCATED,
# STATION_COUNT STATIONS_ATTEMPTED,
# HAUL_COUNT STATIONS_COMPLETED,
# AREA,
# round(((HAUL_COUNT/AREA)1000),2) SAMPLING_DENSITY,
# A.SUMMARY_AREA_DEPTH
# from (
# select INPFC_AREA,
# DEPTH_RANGE,
# round(sum(AREA),0) AREA,
# SUMMARY_AREA_DEPTH -- sum by stratum within a fishing area and depth range
# from (
# select INPFC_AREA,
# MIN_DEPTH|| ' - ' ||MAX_DEPTH DEPTH_RANGE,
# AREA,
# SUMMARY_AREA_DEPTH
# from GOA.GOA_STRATA
# where SURVEY = 'AI'
# )
# group by INPFC_AREA, DEPTH_RANGE, SUMMARY_AREA_DEPTH
# ) a,
# (
# select INPFC_AREA,
# DEPTH_RANGE,
# SUMMARY_AREA_DEPTH,
# count() HAUL_COUNT -- count of hauls successfully completed during survey
# from (
# select INPFC_AREA,
# MIN_DEPTH|| ' - ' ||MAX_DEPTH DEPTH_RANGE,
# SUMMARY_AREA_DEPTH,
# VESSEL,
# CRUISE,
# HAUL
# from GOA.GOA_STRATA A,
# RACEBASE.HAUL B
# where B.REGION = 'AI' and
# B.REGION = A.SURVEY and
# CRUISE = 202201 and
# VESSEL in (176,148) and
# A.STRATUM = B.STRATUM and
# B.ABUNDANCE_HAUL = 'Y' -- with this constraint it is not possible to accidentally double count a station in common across vessels which is a sampling error in itself
# )
# group by INPFC_AREA,DEPTH_RANGE,SUMMARY_AREA_DEPTH
# ) b,
# (
# select INPFC_AREA,
# SUMMARY_AREA_DEPTH,
# DEPTH_RANGE,
# count() STATION_COUNT --count of all "stations" (composite stationid/stratum identities) attempted
# from (
# select INPFC_AREA,
# SUMMARY_AREA_DEPTH,
# MIN_DEPTH|| ' - ' ||MAX_DEPTH DEPTH_RANGE
# from GOA.GOA_STRATA a, (
# select distinct REGION, -- returns all stations sampled regardless of success but does not count repeated attempts at same station
# CRUISE,
# STATIONID,
# STRATUM
# from RACEBASE.HAUL
# where REGION = 'AI' and
# CRUISE = 202201 and
# VESSEL in (176,148) and
# HAUL_TYPE = 3
# ) b
# where B.REGION = A.SURVEY and
# A.STRATUM = B.STRATUM
# )
# group by INPFC_AREA,DEPTH_RANGE,SUMMARY_AREA_DEPTH
# ) c,
# (
# select INPFC_AREA,
# SUMMARY_AREA_DEPTH,
# DEPTH_RANGE,
# count() STATIONS_ALLOCATED -- from initial station allocation undertaken during survey planning phase
# from (
# select INPFC_AREA,
# SUMMARY_AREA_DEPTH,
# MIN_DEPTH|| ' - ' ||MAX_DEPTH DEPTH_RANGE
# from GOA.GOA_STRATA a,
# AI.STATION_ALLOCATION b -- in AI because new stations assigned are id'd by stratum only, this will return new and prev successful stations allocated
# where B.SURVEY = 'AI'
# and B.SURVEY = A.SURVEY
# and A.STRATUM = B.STRATUM
# and B.YEAR = 2022
# )
# group by INPFC_AREA,DEPTH_RANGE,SUMMARY_AREA_DEPTH
# ) d
# where A.INPFC_AREA = B.INPFC_AREA and B.INPFC_AREA = C.INPFC_AREA and C.INPFC_AREA = D.INPFC_AREA and
# A.DEPTH_RANGE = B.DEPTH_RANGE and B.DEPTH_RANGE = C.DEPTH_RANGE and C.DEPTH_RANGE = D.DEPTH_RANGE and
# A.SUMMARY_AREA_DEPTH = B.SUMMARY_AREA_DEPTH and B.SUMMARY_AREA_DEPTH = C.SUMMARY_AREA_DEPTH and
# C.SUMMARY_AREA_DEPTH = D.SUMMARY_AREA_DEPTH
# order by A.SUMMARY_AREA_DEPTH,A.DEPTH_RANGE
# /
```



# Check Table 2 
```{r}
# NOTE: THESE DON'T CURRENTLY WORK; i THINK IT'S A SQL IN R THING, UGH
table2_districts <- RODBC::sqlQuery(channel, "with SURVEY_DISTRICTS as (
select a.*, row_number () over (
partition by survey_district
order by cpue desc) rn
from (select distinct l.inpfc_area survey_district, i.summary_area, s.common_name, (i.mean_wgt_cpue/100) cpue from AI.BIOMASS_INPFC i, RACEBASE.SPECIES s, GOA.GOA_STRATA l
where i.species_code = s.species_code and i.summary_area = l.summary_area and year = 2022 and l.survey = 'AI')) select survey_district, common_name species_name, round(cpue,1) cpue
from SURVEY_DISTRICTS where rn <= 20
order by summary_area, cpue desc
/")

table2_aleutian_districts <- RODBC::sqlQuery(channel, "select * from (
select regulatory_area_name, common_name species_name, round(mean_wgt_cpue/100,1) cpue
from ai.biomass_area a, racebase.species b
where year = 2022 -- year hardcoded should be dynamic
and regulatory_area_name = 'ALEUTIANS' -- regulatory_area_name hardcoded
and a.species_code = b.species_code
order by mean_wgt_cpue desc
)
where rownum <= 20
order by cpue desc
/")

table2_bsai_or_all <- RODBC::sqlQuery(channel, "select * from (
select 'BSAI' area, common_name species_name, round(mean_wgt_cpue/100,1) cpue
from ai.biomass_total a, racebase.species b
where year = 2022 -- year hardcoded should be dynamic
and a.species_code = b.species_code
order by mean_wgt_cpue desc
)
where rownum <= 20
order by cpue desc
/")

# table2_sql <- RODBC::sqlQuery(channel, "select * from table_1_data;
# select distinct 
#     c.inpfc_area, 
#     b.summary_area, 
#     common_name, 
#     round(b.mean_wgt_cpue/100,2) cpue
# from 
#     racebase.species s, 
#     ai.biomass_inpfc b, 
#     goa.goa_strata c
# where 
#     s.species_code = b.species_code and
#     b.year = 2014 and 
#     b.summary_area in (select distinct summary_area from goa.goa_strata where survey = 'AI') and 
#     b.summary_area = c.summary_area
# order by b.summary_area,-round(b.mean_wgt_cpue/100,2)
# /
# 
# select common_name,
# round(mean_wgt_cpue/100,2) cpue
# from ai.biomass_total a, 
# racebase.species b
# where a.survey = 'AI' 
# and a.year = 2014
# and a.species_code = b.species_code
# order by -a.mean_wgt_cpue
# /
# 
# select distinct 
#     b.regulatory_area_name, 
#     common_name, 
#     round(b.mean_wgt_cpue/100,2) cpue
# from 
#     racebase.species s, 
#     ai.biomass_area b
# where 
#     s.species_code = b.species_code and
#     b.year = 2014 and 
#     b.regulatory_area_name = 'ALEUTIANS'
# order by -round(b.mean_wgt_cpue/100,2) 
# /")
# head(table2_sql)

```


```{r}

# Which survey number is it?
(survnumber)
survnumber_sql <- RODBC::sqlQuery(channel, "select count(distinct cruise) survnumber
from race_data.cruises a, race_data.survey_definitions b, race_data.surveys c
where b.survey_name = 'Aleutian Islands Bottom Trawl Survey'
and a.survey_id = c.survey_id
and b.survey_definition_id = c.survey_definition_id")

# What is the number of successfully sampled stations?
(nstations)
nstations_sql <- RODBC::sqlQuery(channel, "select count(distinct hauljoin) nstations
from racebase.haul
where region = 'AI'
and cruise = 202201
and abundance_haul = 'Y'")

# How many stations were assigned?
nstationsassigned_sql <- RODBC::sqlQuery(channel, "select count(*) new_stations from ai.station_allocation where year = 2022 and stationid is null")

nfishlengths_sql <- RODBC::sqlQuery(channel, "select count(*)
from racebase.length
where region = 'AI'
and cruise = 202201
and length_type in (1,5,11)")

nsquidlengths <- RODBC::sqlQuery(channel, "select count(*)
from racebase.length
where region = 'AI'
and cruise = 202201
and length_type=12")

```
# How many stations don't have Marport spread data?

```{r}
no_marport_data_sql <- RODBC::sqlQuery(channel, "select count(*) spread_measured
from racebase.haul
where region = 'AI'
and cruise = 202201
and net_measured = 'Y' -- always and only refers to net spread and indicates whether we modeled it (N) or measured it (Y)
and abundance_haul = 'Y'")
```

# Check summary of trawl effort for a given species - NEED TO TURN THIS INTO A FUNCTION
```{r}
atf_check_second_table_sql <- RODBC::sqlQuery(channel, "select distinct inpfc_area, min_depth||'-'||max_depth depth_range, haul_count, catch_count, mean_wgt_cpue/100 cpue_kg_ha, area_biomass, min_biomass, max_biomass
from goa.goa_strata a, ai.biomass_inpfc_depth b
where a.survey = 'AI'
and b.year = 2022
and b.species_code = 10110
and a.summary_area_depth = b.summary_area_depth
order by inpfc_area desc, depth_range")

```

# Check species richness with Sarah table
```{r}
x <- RODBC::sqlQuery(channel, "select a.cruise, decode(c.inpfc_area, 'Southern Bering Sea','Eastern Aleutians',c.inpfc_area) area_name, count(distinct b.species_code) elasmo_taxon_richness
from racebase.haul a, racebase.catch b, goa.goa_strata c
where a.region = 'AI'
and a.cruise >= 199101
and a.abundance_haul = 'Y'
and a.hauljoin = b.hauljoin
and b.species_code in (
select species_code
from racebase.species
where species_code between 150 and 711 -- sharks and skates
and species_name not like ('%egg%') -- eliminates records of egg cases
)
and a.region = c.survey
and a.stratum = c.stratum
group by a.cruise, decode(c.inpfc_area,'Southern Bering Sea','Eastern Aleutians',c.inpfc_area)
order by a.cruise, elasmo_taxon_richness desc")
ggplot(x, aes(x = CRUISE, y = ELASMO_TAXON_RICHNESS, color = AREA_NAME)) +
  geom_line()
```

# Check table 4 outputs
This is what Ned uses to produce "table 4" (CPUE and biomass by INPFC area and depth, with CIs):
```{r}
 x <- RODBC::sqlQuery(channel, "select a.inpfc_area, a.description, a.min_depth, a.max_depth, b.haul_count, b.catch_count, b.mean_wgt_cpue, b.stratum_biomass, b.min_biomass, b.max_biomass
  from goa.goa_strata a, ai.biomass_Stratum b
  where a.survey = 'AI'
  and a.stratum = b.stratum
  and b.species_code = 10110
  and b.year = 2022
  order by a.description, a.min_depth")
```


## Checks

This script produces an easy-to-read table that compares the values produced in R to the ones produced by SQL queries, which used to be used to produce the data reports. 

```{r}
indiv_values <- data.frame("Variable name" = c("survnumber","nstations"),
                           "Description" = c("description 1","description 2"),
  "Value in previous report year" = c(NA,NA),
"Value this year from R" = c(survnumber,nstations)) %>%
  kableExtra::kable()
```


