---
title: "Check values against SQL query versions of the same thing"
author: "M Siple"
date: "2023-01-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Setup channel to connect to Oracle --------------------------------------
source(here::here("R/setup_channel.R"))
# The setup_channel.R script sets up a channel using your Oracle username and pw.

# Get report settings -----------------------------------------------------
source("R/00_report_settings.R")

# Functions, packages, directories ---------------------------------------------
source("R/01_directories.R")
source("R/02_load_packages.R") 
```


```{r}
# table2_sql <- RODBC::sqlQuery(channel, "select * from table_1_data;
# select distinct 
#     c.inpfc_area, 
#     b.summary_area, 
#     common_name, 
#     round(b.mean_wgt_cpue/100,2) cpue
# from 
#     racebase.species s, 
#     ai.biomass_inpfc b, 
#     goa.goa_strata c
# where 
#     s.species_code = b.species_code and
#     b.year = 2014 and 
#     b.summary_area in (select distinct summary_area from goa.goa_strata where survey = 'AI') and 
#     b.summary_area = c.summary_area
# order by b.summary_area,-round(b.mean_wgt_cpue/100,2)
# /
# 
# select common_name,
# round(mean_wgt_cpue/100,2) cpue
# from ai.biomass_total a, 
# racebase.species b
# where a.survey = 'AI' 
# and a.year = 2014
# and a.species_code = b.species_code
# order by -a.mean_wgt_cpue
# /
# 
# select distinct 
#     b.regulatory_area_name, 
#     common_name, 
#     round(b.mean_wgt_cpue/100,2) cpue
# from 
#     racebase.species s, 
#     ai.biomass_area b
# where 
#     s.species_code = b.species_code and
#     b.year = 2014 and 
#     b.regulatory_area_name = 'ALEUTIANS'
# order by -round(b.mean_wgt_cpue/100,2) 
# /")
# head(table2_sql)

```


```{r}

# Which survey number is it?
(survnumber)
survnumber_sql <- RODBC::sqlQuery(channel, "select count(distinct cruise) survnumber
from race_data.cruises a, race_data.survey_definitions b, race_data.surveys c
where b.survey_name = 'Aleutian Islands Bottom Trawl Survey'
and a.survey_id = c.survey_id
and b.survey_definition_id = c.survey_definition_id")

# What is the number of successfully sampled stations?
(nstations)
nstations_sql <- RODBC::sqlQuery(channel, "select count(distinct hauljoin) nstations
from racebase.haul
where region = 'AI'
and cruise = 202201
and abundance_haul = 'Y'")

# How many stations were assigned?
nstationsassigned_sql <- RODBC::sqlQuery(channel, "select count(*) new_stations from ai.station_allocation where year = 2022 and stationid is null")

nfishlengths_sql <- RODBC::sqlQuery(channel, "select count(*)
from racebase.length
where region = 'AI'
and cruise = 202201
and length_type in (1,5,11)")

nsquidlengths <- RODBC::sqlQuery(channel, "select count(*)
from racebase.length
where region = 'AI'
and cruise = 202201
and length_type=12")

```
# How many stations don't have Marport spread data?

```{r}
no_marport_data_sql <- RODBC::sqlQuery(channel, "select count(*) spread_measured
from racebase.haul
where region = 'AI'
and cruise = 202201
and net_measured = 'Y' -- always and only refers to net spread and indicates whether we modeled it (N) or measured it (Y)
and abundance_haul = 'Y'")
```

# Check summary of trawl effort for a given species - NEED TO TURN THIS INTO A FUNCTION
```{r}
atf_check_second_table_sql <- RODBC::sqlQuery(channel, "select distinct inpfc_area, min_depth||'-'||max_depth depth_range, haul_count, catch_count, mean_wgt_cpue/100 cpue_kg_ha, area_biomass, min_biomass, max_biomass
from goa.goa_strata a, ai.biomass_inpfc_depth b
where a.survey = 'AI'
and b.year = 2022
and b.species_code = 10110
and a.summary_area_depth = b.summary_area_depth
order by inpfc_area desc, depth_range")

```

# Check species richness with Sarah table
```{r}
x <- RODBC::sqlQuery(channel, "select a.cruise, decode(c.inpfc_area, 'Southern Bering Sea','Eastern Aleutians',c.inpfc_area) area_name, count(distinct b.species_code) elasmo_taxon_richness
from racebase.haul a, racebase.catch b, goa.goa_strata c
where a.region = 'AI'
and a.cruise >= 199101
and a.abundance_haul = 'Y'
and a.hauljoin = b.hauljoin
and b.species_code in (
select species_code
from racebase.species
where species_code between 150 and 711 -- sharks and skates
and species_name not like ('%egg%') -- eliminates records of egg cases
)
and a.region = c.survey
and a.stratum = c.stratum
group by a.cruise, decode(c.inpfc_area,'Southern Bering Sea','Eastern Aleutians',c.inpfc_area)
order by a.cruise, elasmo_taxon_richness desc")
ggplot(x, aes(x = CRUISE, y = ELASMO_TAXON_RICHNESS, color = AREA_NAME)) +
  geom_line()
```

# Check table 4 outputs
This is what Ned uses to produce "table 4" (CPUE and biomass by INPFC area and depth, with CIs):
```{r}
 x <- RODBC::sqlQuery(channel, "select a.inpfc_area, a.description, a.min_depth, a.max_depth, b.haul_count, b.catch_count, b.mean_wgt_cpue, b.stratum_biomass, b.min_biomass, b.max_biomass
  from goa.goa_strata a, ai.biomass_Stratum b
  where a.survey = 'AI'
  and a.stratum = b.stratum
  and b.species_code = 10110
  and b.year = 2022
  order by a.description, a.min_depth")
```


## Checks

This script produces an easy-to-read table that compares the values produced in R to the ones produced by SQL queries, which used to be used to produce the data reports. 

```{r}
indiv_values <- data.frame("Variable name" = c("survnumber","nstations"),
                           "Description" = c("description 1","description 2"),
  "Value in previous report year" = c(NA,NA),
"Value this year from R" = c(survnumber,nstations)) %>%
  kableExtra::kable()
```


