-----

## {{spp_name_informal_low}} (*{{spp_name_scientific}}*)

<!-- These are the summary bullet points. -->
- The {{spp_name_informal_sen}} includes {{f2}} and {{f4}}.

-  The {{spp_name_informal_low}} was the `r scales::ordinal({{xth}})` most abundant group caught in the {{year}} {{region}} survey. The total biomass was estimated to be {{species_biomass}} (Table `r officer::run_reference(paste0("table1-","{{species_code}}"))`), which is a {{spp_percent_change}}% {{spp_incr_decr}} from {{compareyr}}.

-   The largest estimated biomass for the {{spp_name_informal_low}} was in the {{inpfc_highest_biomass}} region and the depth range with the largest estimated biomass was {{depth_highest_biomass}}.

-   The highest CPUEs were recorded in the {{inpfc_highest_cpue[1]}} and {{inpfc_highest_cpue[2]}} regions (Table `r officer::run_reference(paste0("table1-","{{species_code}}"))` and Fig. `r officer::run_reference(paste0("cpue-","{{species_code}}"))`).

-   Length compositions and size by depth are not shown for complexes; these data are available upon request.

`r if({{show.text}}){paste0("- ","{{sex_diff_sentence}}") }`

\newpage

```{r echo=FALSE,tab.cap='Summary by survey districts and depth intervals of {{year}} {{region}} trawl effort (number of hauls), number of hauls containing members of the {{spp_name_informal_low}}, and their mean CPUE and biomass estimates.', tab.id=paste0("table1-","{{species_code}}"),  tab.cap.style = "Table caption",tab.align="left"}
table3s_list[["{{ species_code }}"]] |>
  #table3s_list[[as.character(30060)]] |>
   flextable() |>
  theme_vanilla() |>
  fontsize(size = 9, part = "all") |>
  fit_to_width(max_width = 8.25, unit = "in") |>
  align(align = "center", part = "all") |>
  align(j = 1, align = "left", part = "body") |>
  padding(padding = 1, part = "all") |>
  set_table_properties(layout = "autofit") |>
  set_header_labels(
    `Total haul count` = "Total \n haul count",
    `Hauls with positive catch` = "Hauls w/\npositive catch",
    #`CPUE (kg/km2)` = "CPUE\n(kg/km2)",
    `Biomass (t)` = "Biomass\n(t)"
  ) |>
  compose(part = "header", i = 1, j = 5, value = as_paragraph("CPUE\n(kg/km", as_sup("2"), ")"))
```

\newpage

```{r echo=FALSE,tab.cap='Summary by survey district (INPFC area), survey subdistrict, and depth intervals of {{year}} {{region}} survey trawl effort (number of hauls), number of hauls containing members of the {{spp_name_informal_low}}, and their mean CPUE and biomass estimates.', tab.id=paste0("table2-","{{species_code}}"),  tab.cap.style = "Table caption",tab.align="left"}

table4s_list[["{{ species_code }}"]] |>
# table4s_list[[as.character(30060)]] %>%
 flextable() |>
  fix_border_issues() |>
  theme_vanilla() |>
  fontsize(size = 9, part = "all") |>
  fit_to_width(max_width = 8.25, unit = "in") |>
  align(align = "center", part = "all")|>
  align(j = c(1, 5, 6), align = "left", part = "body") |>
  align(i = 1, align = "center", part = "header") |>
  padding(padding = 1, part = "all")  |>
  set_table_properties(layout = "autofit") |>
  set_header_labels(`Total haul count` = "Total \n haul count",
                    `Hauls with positive catch` = "Hauls w/\npositive catch",
                    `CPUE (kg/km2)` = "CPUE\n(kg/km2)",
                    `Biomass (t)` = "Biomass\n(t)") |>
  compose(part = "header", i = 1, j = 5, value = as_paragraph("CPUE\n(kg/km", as_sup("2"), ")"))
```

<!---BLOCK_LANDSCAPE_START--->

```{r echo=FALSE,fig.cap='Catch per unit effort (CPUE, kg/ha; X = no catch) of the {{spp_name_informal_low}} in the {{year}} {{region}} RACE GAP summer bottom trawl survey. Strata are shaded by their maximum depth (darker colors = deeper).', fig.id=paste0("cpue-","{{species_code}}"), tab.cap.style = "Figure Caption",fig.width=10,fig.height = 5.5, dpi=300}
list_cpue_bubbles_strata[["{{species_code}}"]]
```

<!---BLOCK_LANDSCAPE_STOP--->
