\newpage
## {{spp_name_informal_low}} (*{{spp_name_scientific}}*)

<!-- These are the summary bullet points. -->

-   {{spp_name_informal_sen}} was the `r scales::ordinal({{xth}})` most abundant species caught in the {{year}} {{region}} survey. Their total biomass was estimated to be {{species_biomass}} (Table `r officer::run_reference(paste0("table1-","{{species_code}}"))`), which is a {{spp_percent_change}}% {{spp_incr_decr}} from {{compareyr}}.

-   The largest estimated biomass for {{spp_name_informal}} was in the {{nmfs_highest_biomass}} district and the depth range with the largest estimated biomass was {{depth_highest_biomass}}.

-   The highest {{spp_name_informal}} CPUEs were recorded in the {{nmfs_highest_cpue[1]}} and {{nmfs_highest_cpue[2]}} districts (Table `r officer::run_reference(paste0("table1-","{{species_code}}"))` and Fig. `r officer::run_reference(paste0("cpue-","{{species_code}}"))`).

-   On average, the longest individuals were found in the {{region_longest}} region and in a depth range of {{depth_longest}} (Figure `r officer::run_reference(paste0("lengthdepth-","{{species_code}}"))`). Historical length distributions are provided in Figure `r officer::run_reference(paste0("lengthcomp-","{{species_code}}"))`.

`r if({{show.text}}){paste0("- ","{{sex_diff_sentence}}") }`

\newpage

```{r echo=FALSE,tab.cap='Summary by survey districts and depth intervals of {{year}} {{region}} trawl effort (number of hauls), number of hauls containing {{spp_name_informal}}, their mean CPUE and biomass estimates, and average fish weight.', tab.id=paste0("table1-","{{species_code}}"),  tab.cap.style = "Table caption",tab.align="left"}
table3s_list[["{{ species_code }}"]] |>
    # table3s_list[[as.character(30060)]] |>
    flextable() |>
    theme_vanilla() |>
    font(fontname = tablefont, part = "all") |>
    fontsize(size = 10, part = "all") |>
    fit_to_width(max_width = 8.25, unit = "in") |>
    align(align = "center", part = "body") |>
    align(align = "center", part = "header") |>
    align(j = 1, align = "left", part = "body") |>
    padding(padding = 1, part = "all") |>
    set_table_properties(layout = "autofit") |>
    set_header_labels(
      `Total haul count` = "Total \n haul count",
      `Hauls with positive catch` = "Hauls w/\npositive \ncatch",
      `Percent positive tows` = "% \npositive \ntows",
      `Biomass (t)` = "Biomass\n(t)",
      `Average weight (kg)` = "Average \nweight \n(kg)"
    ) |>
    bold(i = 6) |> #bold the row with the All Areas total
    compose(part = "header", i = 1, j = 5, value = as_paragraph("CPUE\n(kg/km", as_sup("2"), ")"))
```

\newpage

```{r echo=FALSE,tab.cap='Summary by area and depth interval of {{year}} {{region}} survey trawl effort (number of hauls), number of hauls containing {{spp_name_informal}}, and their mean CPUE and biomass estimates.', tab.id=paste0("table2-","{{species_code}}"),  tab.cap.style = "Table caption",tab.align="left"}

table4s_list[["{{ species_code }}"]] |>
# table4s_list[[as.character(30060)]] %>%
  flextable() |>
  fix_border_issues() |>
  theme_vanilla() |>
  font(fontname = tablefont, part = "all") |>
  fontsize(size = 10, part = "all") |>
  fit_to_width(max_width = 8.25, unit = "in") |>
  align(align = "center", part = "body")|>
  align(j = c(1, 6, 7), align = "left", part = "body") |>
  align(i = 1, align = "center", part = "header") |>
  padding(padding = 1, part = "all")  |>
  padding(padding.left = 4, padding.right = 4, part = "all") |>
  set_table_properties(layout = "autofit") |>
  set_header_labels(`Total haul count` = "Total \n haul count",
                    `Hauls with positive catch` = "Hauls w/\npositive catch",
                    `Percent hauls with positive catch` = "% \npositive \ntows",
                    `CPUE (kg/km2)` = "CPUE\n(kg/km2)",
                    `Biomass (t)` = "Biomass\n(t)") |>
  compose(part = "header", i = 1, j = 6, value = as_paragraph("CPUE\n(kg/km", as_sup("2"), ")"))
```

<br/>

```{r echo=FALSE,fig.fullwidth=TRUE,dpi=300,fig.cap='Time series of biomass, prevalence in survey hauls, and percent change in biomass of {{spp_name_informal}} in the {{region}} bottom trawl survey from {{species_start_yr}} to {{maxyr}}. The dashed horizontal line indicates the long term average.', fig.id=paste0("threepanel-","{{species_code}}"), fig.width=6.5,fig.height=2, tab.cap.style = "Figure Caption"}
list_3panel_ts[["{{species_code}}"]]
```

<!---BLOCK_LANDSCAPE_START--->

```{r echo=FALSE,fig.cap='Catch per unit effort (CPUE; X = no catch) of {{spp_name_informal}} in the {{year}} {{region}} RACE GAP summer bottom trawl survey. Strata are shaded by their maximum depth (darker colors = deeper).', fig.id=paste0("cpue-","{{species_code}}"), tab.cap.style = "Figure Caption",fig.width=10,fig.height = 5.5, dpi=300}
list_cpue_bubbles_strata[["{{species_code}}"]]
```

<!---BLOCK_LANDSCAPE_STOP--->

```{r echo=FALSE,fig.fullwidth=TRUE,dpi=300,fig.cap='Population length composition of {{spp_name_informal}} in the {{region}} bottom trawl survey between {{species_start_yr}} and {{maxyr}}. The dotted vertical line indicates median length. {{skate_len_sentence}}', fig.id=paste0("lengthcomp-","{{species_code}}"), fig.width=6.5, tab.cap.style = "Figure Caption"}
list_joy_length[["{{species_code}}"]]
```

<br/>

```{r echo=FALSE,fig.fullwidth=TRUE,dpi=300,fig.cap='Length versus depth for {{spp_name_informal}} by survey district in the {{year}} {{region}} bottom trawl survey. Lines represent predictions from a GAM of length by depth (with a random haul effect) added to show trends in length. Shaded bands indicate 95% confidence intervals. Semitransparent black points indicate raw (measured) lengths. The x axis represents the full depth range where {{spp_name_informal}} were collected.', fig.id=paste0("lengthdepth-","{{species_code}}"), fig.width=6.5,fig.height=2,  tab.cap.style = "Figure Caption"}
list_ldscatter[["{{species_code}}"]]
```
