\newpage
## {{spp_name_informal_low}} (*{{spp_name_scientific}}*)

<!-- These are the summary bullet points. For invertebrates, the two bullet points about size are left out, as there are no size comps for things like giant octopus. -->

-  {{spp_name_informal_sen}} was the `r scales::ordinal({{xth}})` most abundant species caught in the {{year}} {{region}} survey. The total biomass of {{spp_name_informal}} in the {{year}} {{survname_long}} bottom trawl survey was estimated to be {{species_biomass}} t (Table \@ref(tab:top-cpue)), which is a {{spp_percent_change}}% {{spp_incr_decr}} from {{compareyr}}.

-  The largest estimated biomass for {{spp_name_informal}} was in the {{nmfs_highest_biomass}} region, and the depth range with the largest estimated biomass was {{depth_highest_biomass}}.

-  The highest CPUEs were recorded in the {{nmfs_highest_cpue[1]}} and {{nmfs_highest_cpue[2]}} regions (Table `r officer::run_reference(paste0("table1-",{{species_code}}))` and Fig. `r officer::run_reference(paste0("cpue-",{{species_code}}))`). 

\newpage
```{r echo=FALSE,tab.cap='Summary by survey districts and depth intervals of {{year}} {{region}} trawl effort (number of trawl hauls), number of hauls containing {{spp_name_informal}}, their mean CPUE and biomass estimates with lower and upper 95% confidence limits (CL), and average individual weight.', tab.id=paste0("table1-",{{species_code}}),  tab.cap.style = "Table caption",tab.align="left"}
table3s_list[[as.character({{ species_code }})]] |>
  # table3s_list[[as.character(30060)]] |>
  flextable() |>
  theme_vanilla() |>
  fontsize(size = 9, part = "all") |>
  fit_to_width(max_width = 8.25, unit = "in") |>
  align(align = "center", part = "all") |>
  align(j = 1, align = "left", part = "body") |>
  padding(padding = 1, part = "all") |>
  set_table_properties(layout = "autofit") |>
  set_header_labels(
    `Total haul count` = "Total \n haul count",
    `Hauls with positive catch` = "Hauls w/\npositive catch",
    #`CPUE (kg/km2)` = "CPUE\n(kg/km2)",
    `Biomass (mt)` = "Biomass\n(mt)"
  ) |>
  bold(i = 6) |> #bold the row with the All Areas total
  compose(part = "header", i = 1, j = 5, value = as_paragraph("CPUE\n(kg/km", as_sup("2"), ")"))
```


\newpage
```{r echo=FALSE,tab.cap='Summary by survey district (INPFC area), survey subdistrict, and depth intervals of {{year}} {{region}} survey trawl effort (number of hauls), number of hauls containing {{spp_name_informal}}, and their mean CPUE and biomass estimates with lower and upper 95% confidence limits (CL).', tab.id=paste0("table2-",{{species_code}}),  tab.cap.style = "Table caption",tab.align="left"}

table4s_list[[as.character(78403)]] |>
  flextable() |>
  fix_border_issues() |>
  theme_vanilla() |>
  fontsize(size = 9, part = "all") |>
  fit_to_width(max_width = 8.25, unit = "in") |>
  align(align = "center", part = "all")|>
  align(j = c(1, 5, 6), align = "left", part = "body") |>
  align(i = 1, align = "center", part = "header") |>
  padding(padding = 1, part = "all")  |>
  set_table_properties(layout = "autofit") |>
  set_header_labels(`Hauls with positive catch` = "Hauls w/\npositive catch",
                    `CPUE (kg/km2)` = "CPUE\n(kg/km2)",
                    `Biomass (t)` = "Biomass\n(mt)")
```

<!---BLOCK_LANDSCAPE_START--->
```{r echo=FALSE,fig.cap='Catch per unit effort (CPUE, kg/ha; X = no catch) of {{spp_name_informal}} in the {{year}} {{region}} RACE GAP summer bottom trawl survey catches.', fig.id=paste0("cpue-",{{species_code}}),  tab.cap.style = "Figure Caption",fig.width=10,fig.height = 5, dpi=300}
list_cpue_bubbles_strata[[as.character({{species_code}})]]
```
<!---BLOCK_LANDSCAPE_STOP--->
