---
title: "2022 Aleutian Islands Biennial Bottom Trawl Survey"
subtitle: "Groundfish Plan Team Meeting, September 2022"
author: "Ned Laman, Bethany Riggle, Alexandra Dowlin, and Margaret Siple"
date: "September 8, 2022"
output: 
  powerpoint_presentation:
    reference_doc: styles_reference.pptx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,dpi=300,fig.width=10)
```

## `r maxyr` Aleutian Islands bottom trawl survey

The `r maxyr` AI bottom trawl survey took place between `r dates_conducted`. The previous AI survey was in `r compareyr`; the 2020 survey was cancelled because of COVID-19. 


## Survey Purpose

To collect standardized and fishery-independent time series of:

- Relative abundance
- Distribution
- Age and biological condition

There are 31 managed species or species groups in the Bering Sea and Aleutian Islands that have stock assessments.

---

## Catch composition

```{r catchcomp}
p2
```

---

# Biomass trends

---


## Shortraker rockfish

```{r biomass1}
list_biomass_ts[[1]]
```

---

## Pacific ocean perch

```{r biomass2}
list_biomass_ts[[2]]
```

---

## Blackspotted rockfish

```{r biomass3}
list_biomass_ts[[3]]
```

---

## Rougheye rockfish

```{r biomass4}
list_biomass_ts[[4]]
```

---

## Atka mackerel

```{r biomass5}
list_biomass_ts[[5]]
```

---

## Walleye pollock

```{r biomass6}
list_biomass_ts[[6]]
```

---

## Pacific cod

```{r biomass7}
list_biomass_ts[[7]]
```

---

## Yellow irish lord

```{r biomass8}
list_biomass_ts[[8]]
```

---

## Sablefish

```{r biomass9}
list_biomass_ts[[9]]
```

---

## Northern rock sole

```{r biomass10}
list_biomass_ts[[10]]
```

---

## Arrowtooth flounder

```{r biomass11}
list_biomass_ts[[11]]
```

---

## Whiteblotched skate 

```{r biomass12}
list_biomass_ts[[12]]
```

---

## Aleutian skate

```{r biomass13}
list_biomass_ts[[13]]
```

---

# CPUE by survey region

---

## Shortraker rockfish

```{r list_cpue_bubbles1}
list_cpue_bubbles[[1]]
```

## Pacific ocean perch

```{r list_cpue_bubbles2}
list_cpue_bubbles[[2]]
```

---

## Blackspotted rockfish

```{r list_cpue_bubbles3}
list_cpue_bubbles[[3]]
```

---

## Rougheye rockfish

```{r list_cpue_bubbles4}
list_cpue_bubbles[[4]]
```

---

## Atka mackerel

```{r list_cpue_bubbles5}
list_cpue_bubbles[[5]]
```

---

## Walleye pollock

```{r list_cpue_bubbles6}
list_cpue_bubbles[[6]]
```

---

## Pacific cod

```{r list_cpue_bubbles7}
list_cpue_bubbles[[7]]
```

---

## Yellow irish lord

```{r list_cpue_bubbles8}
list_cpue_bubbles[[8]]
```

---

## Sablefish

```{r list_cpue_bubbles9}
list_cpue_bubbles[[9]]
```

---

## Northern rock sole

```{r list_cpue_bubbles10}
list_cpue_bubbles[[10]]
```

---

## Arrowtooth flounder

```{r list_cpue_bubbles11}
list_cpue_bubbles[[11]]
```

---

## Whiteblotched skate 

```{r list_cpue_bubbles12}
list_cpue_bubbles[[12]]
```

---

## Aleutian skate

```{r list_cpue_bubbles13}
list_cpue_bubbles[[13]]
```

---

# Length frequencies

---

## Shortraker rockfish

```{r list_length_freq1}
list_length_freq[[1]]
```

## Pacific ocean perch

```{r list_length_freq2}
list_length_freq[[2]]
```

---

## Blackspotted rockfish

```{r list_length_freq3}
list_length_freq[[3]]
```

---

## Rougheye rockfish

```{r list_length_freq4}
list_length_freq[[4]]
```

---

## Atka mackerel

```{r list_length_freq5}
list_length_freq[[5]]
```

---

## Walleye pollock

```{r list_length_freq6}
list_length_freq[[6]]
```

---

## Pacific cod

```{r list_length_freq7}
list_length_freq[[7]]
```

---

## Yellow irish lord

```{r list_length_freq8}
list_length_freq[[8]]
```

---

## Sablefish

```{r list_length_freq9}
list_length_freq[[9]]
```

---

## Northern rock sole

```{r list_length_freq10}
list_length_freq[[10]]
```

---

## Arrowtooth flounder

```{r list_length_freq11}
list_length_freq[[11]]
```

---

## Whiteblotched skate 

```{r list_length_freq12}
list_length_freq[[12]]
```

---

## Aleutian skate

```{r list_length_freq13}
list_length_freq[[13]]
```

---