---
title: "GOA-AI Plan Team Slides"
author: "M Siple"
date: "2022-09-08"
output: 
  powerpoint_presentation:
    reference_doc: styles_reference.pptx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,dpi=300,fig.width=7)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.


## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

---

## Catch composition

```{r catchcomp}
p2
```

---

# Biomass trends

---


## Shortraker rockfish

```{r biomass1}
list_biomass_ts[[1]]
```

---

## Pacific ocean perch

```{r biomass2}
list_biomass_ts[[2]]
```

---

## Blackspotted rockfish

```{r biomass3}
list_biomass_ts[[3]]
```

---

## Rougheye rockfish

```{r biomass4}
list_biomass_ts[[4]]
```

---

## Atka mackerel

```{r biomass5}
list_biomass_ts[[5]]
```

---

## Walleye pollock

```{r biomass6}
list_biomass_ts[[6]]
```

---

## Pacific cod

```{r biomass7}
list_biomass_ts[[7]]
```

---

## Yellow irish lord

```{r biomass8}
list_biomass_ts[[8]]
```

---

## Sablefish

```{r biomass9}
list_biomass_ts[[9]]
```

---

## Northern rock sole

```{r biomass10}
list_biomass_ts[[10]]
```

---

## Arrowtooth flounder

```{r biomass11}
list_biomass_ts[[11]]
```

---

## Whiteblotched skate 

```{r biomass12}
list_biomass_ts[[12]]
```

---

## Aleutian skate

```{r biomass13}
list_biomass_ts[[13]]
```

---

# CPUE by survey region

---

## Shortraker rockfish

