## {{spp_name_informal_sen}} (*{{spp_name_scientific}}*)

{{spp_name_informal_sen}} was the `r scales::ordinal({{xth}})` most abundant species caught in the {{year}} {{region}} survey (Table \@ref(tab:top-cpue)). The highest densities were recorded in the {{top_cpue}} and {{second_top_cpue}} (Figure `r officer::run_reference(paste0("first-",{{species_code}}))` and  Table `r officer::run_reference(paste0("table1-",{{species_code}}))`). {{middle_sentences}} On average, the largest individuals were found in the {{region_largest}} (Figure `r officer::run_reference(paste0("second-",{{species_code}}))`). The estimated total biomass of {{spp_name_informal}} in the `r survname_long` bottom trawl survey was estimated to be {{species_biomass}} t.


\newpage
```{r echo=FALSE,tab.cap='Summary by survey districts and depth intervals of {{year}} {{region}} trawl effort (number of trawl hauls), number of hauls containing {{spp_name_informal}}, their mean CPUE and biomass estimates with lower and upper 95% confidence limits (LCL and UCL, respectively), and average fish weight.', tab.id=paste0("table1-",{{species_code}}),  tab.cap.style = "Table Caption"}
table3s_list[[as.character({{ species_code }})]][,1:9] %>%
  #table3s_list[[as.character(10112)]][,1:9] %>%
  flextable() %>%
  theme_vanilla() %>%
  fontsize(size = 9, part = "all") %>%
  fit_to_width(max_width = 8, unit = "in") %>%
  align(i = 1, align = "center",part = 'header') %>%
  set_caption(
    as_paragraph(
      as_chunk("Summary by survey districts and depth intervals of {{year}} {{region}} trawl effort (number of trawl hauls), number of hauls containing {{spp_name_informal}}, their mean CPUE and biomass estimates with lower and upper 95% confidence limits (LCL and UCL, respectively), and average fish weight.", props = fp_text_default(font.family = "Times New Roman", font.size = 10))
    ),
    word_stylename = "Table Caption"
  ) 
```


\newpage
```{r echo=FALSE,tab.cap='Summary of {{spp_name_informal}} mean catch-per-unit-effort (CPUE) and estimated biomass (t) including the lower and upper 95% confidence limits (LCL and UCL, respectively) from the {{year}} {{region}} bottom trawl survey by stratum (i.e., the composite of survey district, depth interval, and subarea) ordered from highest to lowest CPUE.', tab.id=paste0("table2-",{{species_code}}),  tab.cap.style = "Table Caption"}

table4s_list[[as.character({{ species_code }})]] %>%
# table4s_list[[as.character(30060)]] %>%
  dplyr::mutate_at(.vars = c("Biomass (t)","Lower 95% CI","Upper 95% CI"), biomass_round,
                ) %>%
  dplyr::arrange(`INPFC area`,`Stratum name`,`Depth range (m)`) %>%
  flextable() %>%
  merge_v(j = ~`INPFC area`) %>%
  fix_border_issues() %>%
  theme_vanilla() %>%
  fontsize(size = 9, part = "all") %>%
  fit_to_width(max_width = 8, unit = "in") %>%
  align(i = 1, align = "center",part = 'header') %>%
  set_caption(
    as_paragraph(
      as_chunk("Summary of {{spp_name_informal}} mean catch-per-unit-effort (CPUE) and estimated biomass (t) including the lower and upper 95% confidence limits (LCL and UCL, respectively) from the {{year}} {{region}} bottom trawl survey by stratum (i.e., the composite of survey district, depth interval, and subarea) ordered from highest to lowest CPUE.", props = fp_text_default(font.family = "Times New Roman", font.size = 10))
    ),
    word_stylename = "Table Caption"
  ) %>%
  hline(i = ~ break_position(`INPFC area`), border = cl) 
```

\newpage
\begin{landscape}
```{r echo=FALSE,fig.fullwidth=TRUE,dpi=300,fig.cap='Relative abundance of {{spp_name_informal}} in units of catch-per-unit-effort (CPUE; kg/km^2^) in relation to their mean CPUE (X = no catch) in the {{year}} NMFS AFSC RACE Groundfish Assessment Program’s {{region}} summer bottom trawl survey catches.', fig.id=paste0("first-",{{species_code}}),  tab.cap.style = "Figure Caption"}
list_cpue_bubbles[[as.character({{species_code}})]]
```
\end{landscape}

\newpage
```{r echo=FALSE,fig.fullwidth=TRUE,dpi=300,fig.cap='Population length composition of {{spp_name_informal}} by survey district and depth interval in the {{year}} {{region}} bottom trawl survey, since the start of the survey.', fig.id=paste0("second-",{{species_code}}),  tab.cap.style = "Figure Caption"}
list_joy_length[[as.character({{species_code}})]]
```
