# {{spp_name_informal}} (**{{spp_name_scientific}}**)

{{spp_name_informal}} was the {{xth}} most abundant species caught in the {{year}} {{region}} survey (Table 2). The highest densities were recorded in the `r {{top_cpue_vec}}[1]` and `r {{top_cpue_vec}}[2]` (Figure `r officer::run_reference(paste0("first-",{{species_code}}))` and  Table `r officer::run_reference(paste0("table1-",{{species_code}}))`).  {{middle_sentences}}. 

The largest individuals were found in XXX (INSERT WHERE THESE WERE!) (Figure `r officer::run_reference(paste0("second-",{{species_code}}))`).

```{r echo=FALSE,tab.cap='Test table to make sure I can do both in the same doc', tab.id=paste0("table1-",{{species_code}}),  tab.cap.style = "Table Caption"}
table3s_list[[as.character({{species_code}})]]
```

```{r echo=FALSE,tab.cap='Test table to make sure I can do both in the same doc', tab.id=paste0("table2-",{{species_code}}),  tab.cap.style = "Table Caption"}
table4s_list[[as.character({{species_code}})]]
```

```{r echo=FALSE,fig.cap='First figure in parameterized document -- the figure number is 1 the first time it shows up, and 2 the second time it shows up.', fig.id=paste0("first-",{{species_code}}),  tab.cap.style = "Figure Caption"}
list_cpue_bubbles[[as.character({{species_code}})]]
```

```{r echo=FALSE,fig.cap='Second figure in parameterized document -- the figure number is 2 the first time it shows up, and 4 the second time it shows up.', fig.id=paste0("second-",{{species_code}}),  tab.cap.style = "Figure Caption"}
list_joy_length[[as.character({{species_code}})]]
```


