
\newpage
## {{spp_name_informal_sen}} (*{{spp_name_scientific}}*)

<!-- These are the summary bullet points. -->

-  {{spp_name_informal_sen}} was the `r scales::ordinal({{xth}})` most abundant species caught in the {{year}} {{region}} survey. The total biomass of {{spp_name_informal}} in the {{year}} {{survname_long}} bottom trawl survey was estimated to be {{species_biomass}} mt (Table \@ref(tab:top-cpue)), which is a {{spp_percent_change}}% {{spp_incr_decr}} from {{compareyr}}. 

-  The largest estimated biomass for {{spp_name_informal}} was in the {{inpfc_highest_biomass}} region, and the depth range with the largest estimated biomass was {{depth_highest_biomass}}.

-  The highest CPUEs were recorded in the {{inpfc_highest_cpue[1]}} and {{inpfc_highest_cpue[2]}} regions (Table `r officer::run_reference(paste0("table1-",{{species_code}}))` and Fig. `r officer::run_reference(paste0("cpue-",{{species_code}}))`). 

-  Length distributions by year are provided in Figure `r officer::run_reference(paste0("lengthcomp-",{{species_code}}))` (total survey sample size *N = {{spp_n_length}}*; Fig. `r officer::run_reference(paste0("lengthdepth-",{{species_code}}))`). On average, the longest individuals were found in the {{region_longest}} region and in a depth range of {{depth_longest}}. 

`r if({{show.text}}){paste0("- ","{{sex_diff_sentence}}") }`

\newpage
```{r echo=FALSE,tab.cap='Summary by survey districts and depth intervals of {{year}} {{region}} trawl effort (number of trawl hauls), number of hauls containing {{spp_name_informal}}, their mean CPUE and biomass estimates with lower and upper 95% confidence limits (CL), and average fish weight.', tab.id=paste0("table1-",{{species_code}}),  tab.cap.style = "Table caption",tab.align="left"}
table3s_list[[as.character({{ species_code }})]][,1:9] %>%
  #table3s_list[[as.character(30060)]][,1:9] %>%
  flextable() %>%
  theme_vanilla() %>%
  fontsize(size = 9, part = "all") %>%
  fit_to_width(max_width = 8, unit = "in") %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = 'body') %>%
  padding(padding = 0, part = "all")
```


\newpage
```{r echo=FALSE,tab.cap='Summary by survey district (INPFC area), survey subdistrict, and depth intervals of {{year}} {{region}} survey trawl effort (number of hauls), number of hauls containing {{spp_name_informal}}, and their mean CPUE and biomass estimates with lower and upper 95% confidence confidence limits (CL).', tab.id=paste0("table2-",{{species_code}}),  tab.cap.style = "Table caption",tab.align="left"}

table4s_list[[as.character({{ species_code }})]] %>%
# table4s_list[[as.character(30060)]] %>%
  dplyr::mutate_at(.vars = c("Biomass (t)","Lower 95% CL","Upper 95% CL"), biomass_round) %>%
  flextable() %>%
  fix_border_issues() %>%
  theme_vanilla() %>%
  fontsize(size = 7.5, part = "all") %>%
  align(align = "center", part = "all") %>%
  align(j = c(1,3), align = "left", part = "body") %>%
  align(i = 1, align = "center", part = "header") %>%
  padding(padding = 0, part = "all") %>%
  set_table_properties(layout = "autofit")
```

<!---BLOCK_LANDSCAPE_START--->
```{r echo=FALSE,fig.cap='Relative abundance of {{spp_name_informal}} in units of catch-per-unit-effort (CPUE, kg/ha; X = no catch) in the {{year}} {{region}} RACE GAP summer bottom trawl survey catches.', fig.id=paste0("cpue-",{{species_code}}),  tab.cap.style = "Figure Caption",fig.width=10,fig.height = 5, dpi=300}
list_cpue_bubbles[[as.character({{species_code}})]]
```
<!---BLOCK_LANDSCAPE_STOP--->

```{r echo=FALSE,fig.fullwidth=TRUE,dpi=300,fig.cap='Population length composition of {{spp_name_informal}} in the {{region}} bottom trawl survey since the start of the sampling stanza. The dotted vertical line indicates median length. {{combo_id_sentence}}', fig.id=paste0("lengthcomp-",{{species_code}}), fig.width=6.5, tab.cap.style = "Figure Caption"}
list_joy_length[[as.character({{species_code}})]]
```
<br/>
```{r echo=FALSE,fig.fullwidth=TRUE,dpi=300,fig.cap='Length versus depth for {{spp_name_informal}} by survey district in the {{year}} {{region}} bottom trawl survey. Lines represent a GAM of length by depth with a random haul effect, added to show trends in length. Shaded bands indicate 95% confidence intervals. Black points indicate raw (measured) lengths, not expanded to the full population.', fig.id=paste0("lengthdepth-",{{species_code}}), fig.width=6.5,fig.height=2,  tab.cap.style = "Figure Caption"}
list_ldscatter[[as.character({{species_code}})]]
```
