
\newpage
## {{spp_name_informal_sen}} (*{{spp_name_scientific}}*)

<br />

<!-- These are the summary bullet points. -->

-  {{spp_name_informal_sen}} was the `r scales::ordinal({{xth}})` most abundant species caught in the {{year}} {{region}} survey (Table \@ref(tab:top-cpue)). 

-  The total biomass of {{spp_name_informal}} in the {{year}} {{survname_long}} bottom trawl survey was estimated to be {{species_biomass}} t. The largest estimated biomass for {{spp_name_informal}} was in the {{inpfc_highest_biomass}} region, and the depth range with the largest estimated biomass was {{depth_highest_biomass}}.

-  The highest densities were recorded in the {{inpfc_highest_cpue}} and {{inpfc_2nd_highest_cpue}} regions (Fig. `r officer::run_reference(paste0("cpue-",{{species_code}}))` and  Table `r officer::run_reference(paste0("table1-",{{species_code}}))`). 

-  On average, the largest individuals were found in the {{region_largest}} region and in a depth range of {{depth_largest}} (total survey sample size *N = {{spp_n_length}}*; Fig. `r officer::run_reference(paste0("lengthdepth-",{{species_code}}))`). Length distributions by year are provided in Figure `r officer::run_reference(paste0("lengthcomp-",{{species_code}}))`.






\newpage
```{r echo=FALSE,tab.cap='Summary by survey districts and depth intervals of {{year}} {{region}} trawl effort (number of trawl hauls), number of hauls containing {{spp_name_informal}}, their mean CPUE and biomass estimates with lower and upper 95% confidence limits, and average fish weight.', tab.id=paste0("table1-",{{species_code}}),  tab.cap.style = "Table Caption",tab.align="left"}
table3s_list[[as.character({{ species_code }})]][,1:9] %>%
  #table3s_list[[as.character(30060)]][,1:9] %>%
  flextable() %>%
  theme_vanilla() %>%
  fontsize(size = 9, part = "all") %>%
  fit_to_width(max_width = 8, unit = "in") %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = 'body') %>%
  padding(padding = 0, part = "all") %>%
  set_caption(
    as_paragraph(
      as_chunk("Summary by survey districts and depth intervals of {{year}} {{region}} trawl effort (number of trawl hauls), number of hauls containing {{spp_name_informal}}, their mean CPUE and biomass estimates with lower and upper 95% confidence limits, and average fish weight.", props = fp_text_default(font.family = "Times New Roman", font.size = 10))
    ),
    word_stylename = "Table Caption"
  ) 
```


\newpage
```{r echo=FALSE,tab.cap='Summary by survey district (INPFC area), survey subdistrict, and depth intervals of {{year}} {{region}} survey trawl effort (number of hauls), number of hauls containing {{spp_name_informal}}, and their mean CPUE and biomass estimates with lower and upper 95% confidence intervals (CI).', tab.id=paste0("table2-",{{species_code}}),  tab.cap.style = "Table Caption",tab.align="left"}

table4s_list[[as.character({{ species_code }})]] %>%
# table4s_list[[as.character(30060)]] %>%
  dplyr::mutate_at(.vars = c("Biomass (t)","Lower 95% CI","Upper 95% CI"), biomass_round) %>%
  flextable() %>%
  fix_border_issues() %>%
  theme_vanilla() %>%
  fontsize(size = 7.5, part = "all") %>%
  align(align = "center", part = "all") %>%
  align(j = c(1,3), align = "left", part = "body") %>%
  align(i = 1, align = "center", part = "header") %>%
  # set_caption(
  #   as_paragraph(
  #     as_chunk("Summary of {{spp_name_informal}} mean catch-per-unit-effort (CPUE) and estimated biomass (t) including the lower and upper 95% confidence intervals (CI) from the {{year}} {{region}} bottom trawl survey by stratum (i.e., the composite of survey district, depth interval, and subarea) ordered from highest to lowest CPUE.", props = fp_text_default(font.family = "Times New Roman", font.size = 10))
  #   ),
  #   word_stylename = "Table Caption"
  # ) %>%
  padding(padding = 0, part = "all") %>%
  set_table_properties(layout = "autofit")
```

<!---BLOCK_LANDSCAPE_START--->
```{r echo=FALSE,fig.fullwidth=TRUE,dpi=300,fig.cap='Relative abundance of {{spp_name_informal}} in units of catch-per-unit-effort (CPUE, kg/ha; X = no catch) in the {{year}} NMFS-AFSC-RACE Groundfish Assessment Program’s {{region}} summer bottom trawl survey catches.', fig.id=paste0("cpue-",{{species_code}}),  tab.cap.style = "Figure Caption",fig.width=10}
list_cpue_bubbles[[as.character({{species_code}})]]
```
<!---BLOCK_LANDSCAPE_STOP--->

```{r echo=FALSE,fig.fullwidth=TRUE,dpi=300,fig.cap='Population length composition of {{spp_name_informal}} in the {{region}} bottom trawl survey since the start of the sampling stanza. The dotted vertical line indicates median length. {{combo_id_sentence}}', fig.id=paste0("lengthcomp-",{{species_code}}), fig.width=6.5, tab.cap.style = "Figure Caption"}
list_joy_length[[as.character({{species_code}})]]
```

```{r echo=FALSE,fig.fullwidth=TRUE,dpi=300,fig.cap='Length versus depth for {{spp_name_informal}} by survey district in the {{year}} {{region}} bottom trawl survey. Lines represent locally estimated scatterplot smoothing (LOESS) smooths added to show trends in length. Shaded bands indicate 95% confidence intervals. Data shown are raw (unexpanded) lengths.', fig.id=paste0("lengthdepth-",{{species_code}}), fig.width=6.5,fig.height=2,  tab.cap.style = "Figure Caption"}
list_ldscatter[[as.character({{species_code}})]]
```
