## {{spp_name_informal}} (*{{spp_name_scientific}}*)

{{spp_name_informal}} was the `r scales::ordinal({{xth}})` most abundant species caught in the {{year}} {{region}} survey (Table 2). The highest densities were recorded in the {{top_cpue}} and {{second_top_cpue}} (Figure `r officer::run_reference(paste0("first-",{{species_code}}))` and  Table `r officer::run_reference(paste0("table1-",{{species_code}}))`). {{middle_sentences}} On average, the largest individuals were found in the {{region_largest}} (Figure `r officer::run_reference(paste0("second-",{{species_code}}))`). The estimated total biomass of {{spp_name_informal}} in the `r survname_long` bottom trawl survey was estimated to be {{species_biomass}} t.

\newpage
```{r echo=FALSE,tab.cap='Summary by survey districts and depth intervals of {{year}} {{region}} trawl effort (number of trawl hauls), number of hauls containing {{spp_name_informal}}, their mean CPUE and biomass estimates with lower and upper 95% confidence limits (LCL and UCL, respectively), and average fish weight.', tab.id=paste0("table1-",{{species_code}}),  tab.cap.style = "Table Caption"}
table3s_list[[as.character({{ species_code }})]] %>%
  #table3s_list[[as.character(30060)]] %>%
  
  flextable() %>%
  theme_vanilla() %>%
  fontsize(size = 8, part = "all") %>%
  fit_to_width(max_width = 8, unit = "in") %>%
  set_caption(
    as_paragraph(
      as_chunk("Summary by survey districts and depth intervals of {{year}} {{region}} trawl effort (number of trawl hauls), number of hauls containing {{spp_name_informal}}, their mean CPUE and biomass estimates with lower and upper 95% confidence limits (LCL and UCL, respectively), and average fish weight.", props = fp_text_default(font.family = "Times New Roman", font.size = 10))
    ),
    word_stylename = "Table Caption"
  ) %>%
  width(j = 1, width = 1.75, unit = "in") %>%
  width(j = 2, width = 1, unit = "in") %>%
  width(j = 3, width = 0.7, unit = "in") %>%
  width(j = 4, width = 0.7, unit = "in") %>%
  width(j = 5, width = 0.7, unit = "in") %>%
  width(j = 6, width = 0.7, unit = "in") %>%
  width(j = 7, width = 0.7, unit = "in") %>%
  width(j = 8, width = 0.7, unit = "in") %>%
  width(j = 9, width = 0.7, unit = "in") %>%
  line_spacing(space = 0.5)
```


\newpage
```{r echo=FALSE,tab.cap='Summary of {{spp_name_informal}} mean catch-per-unit-effort (CPUE) and estimated biomass (t) including the lower and upper 95% confidence limits (LCL and UCL, respectively) from the {{year}} {{region}} bottom trawl survey by stratum (i.e., the composite of survey district, depth interval, and subarea) ordered from highest to lowest CPUE.', tab.id=paste0("table2-",{{species_code}}),  tab.cap.style = "Table Caption"}
table4s_list[[as.character({{ species_code }})]] %>%
# table4s_list[[as.character(30060)]] %>%
  # mutate(`CPUE (kg/ha)`= round(`CPUE (kg/ha)`,digits = 1)) %>%
  # mutate(`Biomass (t)`= round(`Biomass (t)`,digits = 0)) %>% #
  # mutate(`Lower 95% CI`= round(`Lower 95% CI`,digits = 0)) %>%
  # mutate(`Upper 95% CI`= round(`Upper 95% CI`,digits = 0)) %>%
  flextable() %>%
  theme_vanilla() %>%
  fontsize(size = 7.5, part = "all") %>%
  fit_to_width(max_width = 8, unit = "in") %>%
  set_caption(
    as_paragraph(
      as_chunk("Summary of {{spp_name_informal}} mean catch-per-unit-effort (CPUE) and estimated biomass (t) including the lower and upper 95% confidence limits (LCL and UCL, respectively) from the {{year}} {{region}} bottom trawl survey by stratum (i.e., the composite of survey district, depth interval, and subarea) ordered from highest to lowest CPUE.", props = fp_text_default(font.family = "Times New Roman", font.size = 10))
    ),
    word_stylename = "Table Caption"
  ) %>%
  width(j = 1, width = 1.3, unit = "in") %>%
  width(j = 2, width = 0.7, unit = "in") %>%
  width(j = 3, width = 2, unit = "in") %>%
  width(j = 4, width = 0.6, unit = "in") %>%
  width(j = 5, width = 0.5, unit = "in") %>%
  width(j = 6, width = 0.5, unit = "in") %>%
  width(j = 7, width = 0.5, unit = "in") %>%
  width(j = 8, width = 0.5, unit = "in") %>%
  width(j = 9, width = 0.5, unit = "in") %>%
  line_spacing(space = 0.5)
```


\newpage
```{r echo=FALSE,fig.fullwidth=TRUE,dpi=300,fig.cap='Distribution and relative abundance of {{spp_name_informal}} from the {{year}} {{region}} bottom trawl survey across the a) eastern, b) central, and c) western archipelago.', fig.id=paste0("first-",{{species_code}}),  tab.cap.style = "Figure Caption"}
list_cpue_bubbles[[as.character({{species_code}})]]
```

<br />

```{r echo=FALSE,fig.fullwidth=TRUE,dpi=300,fig.cap='Population length composition of {{spp_name_informal}} by survey district and depth interval in the {{year}} {{region}} bottom trawl survey, since the start of the survey.', fig.id=paste0("second-",{{species_code}}),  tab.cap.style = "Figure Caption"}
list_joy_length[[as.character({{species_code}})]]
```


