## {{spp_name_informal}} (*{{spp_name_scientific}}*)

{{spp_name_informal}} was the `r scales::ordinal({{xth}})` most abundant species caught in the {{year}} {{region}} survey (Table 2). The highest densities were recorded in the {{top_cpue}} and {{second_top_cpue}} (@fig-first-{{species_code}}) and  @tab-table1-{{species_code}}. {{middle_sentences}}. 

The largest individuals were found in XXX (INSERT WHERE THESE WERE!) (@fig-second-{{species_code}}. The total biomass of {{spp_name_informal}} was estimated to be (FILL THIS IN!)

```{r echo=FALSE}
#| label: table1-{{species_code}}
#| tbl-cap: 'Summary by survey districts and depth intervals of {{year}} {{region}} trawl effort (number of trawl hauls), number of hauls containing {{spp_name_informal}}, their mean CPUE and biomass estimates with lower and upper 95% confidence limits (LCL and UCL, respectively), and average fish weight.'
table3s_list[[as.character({{species_code}})]]
```

```{r echo=FALSE}
#| label: table2-{{species_code}}
#| tbl-cap: 'Summary of {{spp_name_informal}} mean catch-per-unit-effort (CPUE) and estimated biomass (t) including the lower and upper 95% confidence limits (LCL and UCL, respectively) from the {{year}} {{region}} bottom trawl survey by stratum (i.e., the composite of survey district, depth interval, and subarea) ordered from highest to lowest CPUE.'
table3s_list[[as.character({{species_code}})]]
```


```{r echo=FALSE,fig.width=6.5}
#| label: first-{{species_code}}
#| fig-cap: 'Distribution and relative abundance of {{spp_name_informal}} from the {{year}} {{region}} bottom trawl survey across the a) eastern, b) central, and c) western archipelago.'
list_cpue_bubbles[[as.character({{species_code}})]]
```

```{r echo=FALSE,fig.width=6.5}
#| label: second-{{species_code}}
#| fig-cap: 'Population length composition of {{spp_name_informal}} by survey district and depth interval in the {{year}} {{region}} bottom trawl survey, since the start of the survey.'
list_cpue_bubbles[[as.character({{species_code}})]]
```

